---
title: "IMBD Ratings"
author: "me"
date: "20/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Do Spielberg and Burton have the same IMBD ratings? 

Null hypothesis: Steven Spielberg and Tim Burton have the same IMDB Ratings. 

Alternative hypothesis: Steven Spielberg and Tim Burton do not have the same IMDB Ratings 

```{r load-libraries, include=TRUE, message=FALSE, warning=FALSE}

library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(GGally)
library(readxl)
library(here)
library(skimr)
library(janitor)
library(broom)
library(tidyquant)
library(infer)
library(openintro)
library(tidyquant)
library(lubridate)
```

First, let's read the movies.csv file which contains all the movies and take a look at the data through glimpse.

```{r load-movies-data, include=TRUE, message=FALSE, warning=FALSE}
movies <- read_csv(here::here("Theme copy", "data", "movies.csv"))
glimpse(movies)


```

Then, we'll proceed with the following:

```{r movie_plots, include=TRUE, message=FALSE, warning=FALSE}

##load the data and arrange in order by director to get an overview 
df <- movies %>%
      count(director) %>%
      arrange(desc(n))
  
df 

#filter the movies data to see only data for Spielberg and Burton, then summarise by rating mean, SD, count, Se, t_critical, Rating_lower and Rating_upper, and plot in a table
StevenTimRatings <- movies %>%
                    group_by(director) %>%
                    filter(director %in% c("Steven Spielberg", "Tim Burton")) %>%
                    summarise(Rating_Mean = mean(rating, na.rm = TRUE),
                              Rating_SD = sd(rating, na.rm = TRUE),
                              Rating_count = n(),
                              Rating_Se = Rating_SD/sqrt(Rating_count),
                              t_critical = qt(0.975, Rating_count - 1),
                              Rating_lower = Rating_Mean - Rating_Se * t_critical,
                              Rating_upper = Rating_Mean + Rating_Se * t_critical) 

StevenTimRatings #print

#plot the errorbar 
Ratings_CI <- ggplot(StevenTimRatings, aes(x=Rating_Mean, 
                                          y = reorder(director,Rating_Mean),
                                          xmin = Rating_lower, 
                                          xmax = Rating_upper))+
              geom_errorbar(aes(xmin = Rating_lower, 
                                xmax = Rating_upper, 
                                colour = director, 
                                fill = director), 
                                width = 0.2, 
                                size = 1.5)+
              geom_point(size = 3, shape = 16)+
              geom_rect(xmin = 7.27, 
                        xmax = 7.33, 
                        ymin = 0, 
                        ymax = 10, 
                        fill = "grey", 
                        aes(alpha = 0.5))+
              geom_text(aes(label = round(Rating_lower, 2)), 
                            hjust = 4, 
                            vjust = - 1) +
              geom_text(aes(label = round(Rating_upper, 2)), 
                            hjust = - 4, 
                            vjust = - 1) +
              geom_text(aes(label = round(Rating_Mean, 2)), 
                            size = 5, 
                            hjust = 0.4, 
                            vjust = -1)+
              labs (title = "Do Spielberg and Burton have the same mean IMBD ratings?",
                    subtitle = "95% confidence intervals overlap",
                    y=NULL,
                    x = "Mean IMBD Rating")+
              theme_bw() +
              theme(legend.position = "none") 

Ratings_CI

Spielberg_rating <- movies %>%
  filter(director == "Steven Spielberg") %>%
  select(rating)
  
Burton_rating <- movies %>%
  filter(director == "Tim Burton") %>%
  select(rating)

t.test(Spielberg_rating,Burton_rating)

SteveTimR <- movies %>% 
  select(rating, director) %>% 
  filter(director %in% c("Tim Burton", "Steven Spielberg")) 

#calculate the difference in means
diff_means <- SteveTimR %>%
  specify(rating ~ director) %>%
  calculate(stat = "diff in means", order = c("Tim Burton", "Steven Spielberg"))

#use infer package to generate 1000 reps and calculate difference in means
infer_ratings <- movies %>%
  filter(director == "Steven Spielberg" | director == "Tim Burton") %>%
  specify(rating ~ director) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("Steven Spielberg", "Tim Burton"))

#plot date
ggplot(data = infer_ratings, aes(x = stat)) +
  geom_histogram()

#visualise infer_ratings
infer_ratings %>% visualize() +
  shade_p_value(obs_stat = diff_means, direction = "two-sided")

#get p value
infer_ratings %>%
  get_p_value(obs_stat = diff_means, direction = "two_sided")
  

```


