---
title: "Weather Anomalies"
author: "me"
date: "20/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## How much have temperatures changed over the past century?

First we load all the necessary libraries for this analysis: 

```{r load-libraries, include=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)  
library(mosaic)
library(ggthemes)
library(lubridate)
library(here)
library(skimr)
library(janitor)
library(httr)
library(readxl)
library(vroom)
```

Then we check out the data provided by NASA through the link below and skip NA variables. 

```{r weather_data, include=TRUE, message=FALSE, warning=FALSE}

weather <- 
  read_csv("https://data.giss.nasa.gov/gistemp/tabledata_v3/NH.Ts+dSST.csv", 
           skip = 1, 
           na = "***")

```

Further, we use the pivot function to adapt the data to our needs.

```{r tidyweather, include=TRUE, message=FALSE, warning=FALSE}
tidyweather <- weather %>% 
  select(Year, Jan:Dec) %>% 
  pivot_longer(cols="Jan":"Dec", names_to="Month", values_to="delta")
```

Now, we'll use the mutate function to further adapt the tidyweather dataframe. 

```{r scatter_plot, include=TRUE, message=FALSE, warning=FALSE}

tidyweather <- tidyweather %>%
  mutate(date = ymd(paste(as.character(Year), Month, "1")), #Paste it as Year, Month, Date 
         month = month(date, label=TRUE), #label it
         year = year(date)) 

ggplot(tidyweather, aes(x=date, y = delta))+ #create the ggplot graph
  geom_point()+
  geom_smooth(color="red") + 
  theme_bw() +
  labs (
    title = "Weather Anomalies"
  )

```

We can see a slight upward trend over the first half of the 20th century, and a rather steep increase from the 1970s on. Note the outliers in recent years! 




